---
title: "Análisis Exploratorio y Clusterización de Pacientes con Enfermedad Cardíaca"
author:
  - "Sebastián Flores Figueroa"
  - "Jeriel Fonseca Ramirez"
  - "Roberto Gonzalez Gomez"
  - "Isaac Rodríguez Zúñiga"
  - "Gabriel Aaron Solano Molina"
---
---
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    number_sections: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style>

body {
  background-color: #E6F4F8;
  color: #1A2B32;
  font-family: Arial, Helvetica, sans-serif;
}

h1.title {
  color: #D32F2F;
  font-weight: bold;
  text-align: center;
}

h1, h2, h3 {
  color: #1A2B32;
  font-weight: bold;
}

h2 {
  border-bottom: 3px solid #D32F2F;
  padding-bottom: 6px;
  margin-top: 30px;
}

.nav-pills > li > a {
  color: #1A2B32;
  font-weight: bold;
}

.nav-pills > li.active > a,
.nav-pills > li.active > a:focus,
.nav-pills > li.active > a:hover {
  background-color: #D32F2F;
  color: white;
}

pre {
  border-left: 5px solid #4FC3F7;
  border-radius: 6px;
}

.card-heart {
  background-color: white;
  border-left: 6px solid #D32F2F;
  padding: 15px;
  margin: 15px 0;
  border-radius: 10px;
  box-shadow: 0px 2px 8px rgba(0,0,0,0.08);
}

</style>

```{r child-intro, child='secciones/00-info-general.Rmd'}

```


```{r child-limpieza, child='secciones/01-limpieza.Rmd'}

```


```{r child-eda, child='secciones/02-eda.Rmd'}

```


```{r child-pca, child='secciones/03-pca.Rmd'}

```


```{r child-clustering, child='secciones/04-clustering.Rmd'}

```


```{r child-resultados, child='secciones/05-resultados.Rmd'}

```


```{r child-conclusiones, child='secciones/06-conclusiones.Rmd'}

```
        